ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-05-08 paper/wish/wsc15paper.tex
5-8-15

% AUTHOR: Enter the title, all letters in upper case
\title{ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE: 
%THE NON-NORMAL KNOWN VARIANCE CASE}
THE GENERAL DISTRIBUTION  KNOWN VARIANCE CASE}

@@

There are many applications where we have to choose the best alternative
among a finite number of simulated alternatives. For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$. 
This is called the ranking and selection problem.
% In such ranking and selection problems, we must decide how many samples we need to accurately find the alternative with the largest mean. 
A good procedure for addressing this problem should be both efficient and accurate, i.e. it should balance the number of samples it takes with the quality of its selection.

@@

A good IZ procedure satisfies the IZ guarantee and requires as few samples as possible.
The first IZ procedures presented in \citeN{Bechhofer:1954}, \citeN{Paulson:01}, \citeN{Fabian}, \citeN{Rinott},
\citeN{Harmann:1988}, \citeN{hartmann:sequential}, \citeN{Paulson:1994} 
satisfy the IZ guarantee, but they usually take too many samples when there are many alternatives,
in part because they are conservative: their probability of correct selection (PCS) is much
larger than the probability specified by the user \cite{Kim:Conserv}. One reason for this
is that these procedures use Bonferroni's inequality, which leads then to sample more
than necessary. The Bonferonni-based bounds underlying these procedures become looser, and the tendency to take more samples than necessary increases, as the number of alternatives grow.
More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
\citeN{Hong}, and they improve performance but they still
use Bonferroni's inequality, and so the methods are inefficient
when there are many alternatives. Procedures in \citeN{kim:2011},
\citeN{dieker:2012} do not use Bonferroni's inequality 
when there are only three alternatives, but again use Bonferroni's inequality when 
comparing more than three alternatives.

@@

To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.  Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \cite{Frazier:BIZ}.
We conjecture that a proof technique similar to the one presented here can be used to show asymptotic validity of the BIZ procedure when
the variances are unknown, and we present numerical experiments that support this belief. 
% \citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
% Our proof shares some similarities since we both use a central limit theorem.

@@

Ranking and Selection is a problem where we have to select the best system
among a finite set of alternatives, i.e. the system with the largest
mean. The method selects a system as the best based on the samples
that are observed sequentially over time. We suppose that samples
are identically distributed and independent, over time and across alternatives, and
each alernative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.

@@

The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given below.  It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$.
$B_{x}$ controls the number of samples taken from system $x$ in
each stage. The procedure presented is a slightly modification of the original BIZ 
procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.

@@

This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See  \citeN{Frazier:BIZ}).

@@

% Thus, we can see the selection decision resulting from BIZ as being closely app

@@

\begin{lemma}
% For each $x\in\left\{ 1\ldots,k\right\} $, we define
% \[
% % \mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
% \]
% where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
$x$. 
Let $x\in\left\{ 1\ldots,k\right\} $, then
\[
\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
\]
as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
is a standard Brownian motion.
\end{lemma}

@@

% Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$ and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$, consequently the following natural step is to generalize the continuous-time procedure for the heterogeneous variance setting, see Appendix B, to the space $D\left[0,\infty\right)^{k}$. 
To accomplish the first part, for each $F\in D\left[0,\infty\right)^{k}$, 
we define $q_{tx}^{F,\delta}\left(A\right)$ as
\[
q_{tx}^{F,\delta}\left(A\right)=q'\left(\left(F_{x}\left(t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Note that if we replace $F$ by $\mathcal{C}\left(\delta,t\right)$,
we get $q_{tx}\left(A\right)$ in \eqref{eq:q}.   
% In this sense, 
% we consider to be $q_{tx}^{F,\delta}\left(A\right)$ a ``non-centralized'' version of $F$.

To accomplish the second and third parts, we define
$f\left(F,\delta\right)$ to be obtained by applying the BIZ selection map $h$ to the process
$\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$, and then reporting whether the selection was correct.
More precisely, $f(F,\delta)$ is defined to be
% Using the
% continuous-time procedure for the heterogeneous variance setting with
% the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
% we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
% Since we are interested in the right selection, ( i.e. in choosing
% $k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
% function 
\begin{eqnarray*}
f\left(F,\delta\right) & = & \begin{cases}
    1 & \text{if $h\left(\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
0 & \text{otherwise.}
\end{cases}
\end{eqnarray*}
 % Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.

%We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
%looks like the right or wrong selection decision of an algorithm that
%depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
%and this will give us the proof because we will be able to use the
%theory developed by Frazier (2014) to prove the theorem. Thus, the
We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ} 
% to a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
to a transformed problem that does not depend on $\delta$.

We construct $g$ analogously to $f(\cdot,\delta)$, but we replace the path $q_{tx}^{F,\delta}$ used in the construction of $f(\cdot,\delta)$ by a new path $q_{tx}^{F}$ that doesn't depend on $\delta$, and is obtained by taking the limit as $\delta\to0$.  This path is
% Going back to the proof outline, 
% the next step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
% when $\delta$ goes to zero, which we denote $q_{tx}^{F}\left(A\right)$, 
% and is equal to
\[
q_{tx}^{F}\left(A\right):=\mbox{exp}\left(\frac{F_{x}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x}\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{F_{x'}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x^{'}}\right).
\]
Then, $g$ is defined to be
 %Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
%we define the new functions
\begin{eqnarray*}
g\left(F\right) & = & \begin{cases}
    1 & \text{if $h\left(\left(q_{tx}^{F}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
0 & \text{otherwise.}
\end{cases}
\end{eqnarray*}

@@

% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero. Then we can use the continuous-time BIZ algorithm in the limit, i.e. we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}. 
The following lemma shows that the difference in the correct selection events obtained from applying the BIZ selection map $h$ to the discrete-time and continuous-time versions of $q_{tx}(A)$ vanish as $\delta$ goes to $0$.
A proof of Lemma~\ref{l:interpolation} may be found in a full version of this paper \cite{fullpaper}.

\begin{lemma}
% If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
% distributed with finite variance and independent, over time and across alternatives, then
    $\lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
 \mathbb{P}\left(
 f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
 \right)$.

@@

%By the comments given at the beginning of this section, we know that
%we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by

%\[
%q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
%\]
%where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
%by
%\[
%q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
%\]
%where $t\in\mathbb{N}$.
%
%Now, we define
%\begin{eqnarray*}
%%\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\} 
%\end{eqnarray*}
% The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
% which are defined as

% Maybe some of this goes into the proof of the new lemma
\[
% \tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
\]

% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero. Then we can use the continuous-time BIZ algorithm in the limit, i.e. we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}.

% and allows us to use Theorem~5.5 of \citeN{billingsley:convergence}.

@@

Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration. Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $n_{0}=0$. Figure ~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied, and the PCS approaches $P^*$ as $\delta$ goes to zero. When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.

\begin{figure}[h]
  \centering
   \begin{subfigure}[b]{0.3\textwidth}
      \centering
       \includegraphics[width=\textwidth]{plot5.pdf}
    \caption{
    \label{fig: tahi3}}
   \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{unknown.pdf}
             \caption{
    \label{fig: tahi2}}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{plot3.pdf}
    \caption{ \label{fig: tahi}}
    \end{subfigure}
    \caption{(a)  Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero. (b) Unknown variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be satisfied in all the cases, we can just increment $n_{0}$. (c) Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to illustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
\label{fig:tahi10}}
\end{figure}

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.

We should note that
this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
we can just increment the parameter $n_{0}$.

Now, we consider a pathological case when the variances are known. Specifically, we consider a slippage configuration 
with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
This configurations was specially chosen to illustrate our theorem, and so it is harder than typical configurations.
In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
have run the algorithm with $n_{0}>0$, and the BIZ algorithm would have worked well even in this pathological example. 
Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast.

@@

We have proved the asymptotic validity of the Bayes-inspired Zone
procedure \cite{Frazier:BIZ} when the variances are known, which is a
new sequential elimination procedure. This algorithm is relevant because
it takes fewer samples than other IZ procedures, especially for problems
with large numbers of alternatives. Even though this proof does not
guarantee that the algorithm will work for any sample, we know that
it will work if the alternatives are not very different, which are
the most difficult cases.

>>>>

% AUTHOR: Enter the title, all letters in upper case
\title{ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE: 
%THE NON-NORMAL KNOWN VARIANCE CASE}
THE NON-NORMAL KNOWN VARIANCE CASE}

@@

There are many applications where we have to choose the best alternative
among a finite number of simulated alternatives. For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$. 
This is called the ranking and selection problem.
A good procedure for addressing this problem should be both efficient and accurate, i.e. it should balance the number of samples it takes with the quality of its selection.

@@

A good IZ procedure satisfies the IZ guarantee and requires as few samples as possible.
The first IZ procedures presented in \citeN{Bechhofer:1954}, \citeN{Paulson:01}, \citeN{Fabian}, \citeN{Rinott},
\citeN{Harmann:1988}, \citeN{hartmann:sequential}, \citeN{Paulson:1994} 
satisfy the IZ guarantee, but they usually take too many samples when there are many alternatives,
in part because they are conservative: their probability of correct selection (PCS) is much
larger than the probability specified by the user \cite{Kim:Conserv}. One reason for this
is that these procedures use Bonferroni's inequality, which leads then to sample more
than necessary. The Bonferonni-based bounds underlying these procedures become looser, and the tendency to take more samples than necessary increases, as the number of alternatives grow.
More recently, new algorithms were developed in \citeN{Kim:2001}, \shortciteN{Goldsman:2002}, 
\citeN{Hong}, and they improve performance but they still
use Bonferroni's inequality, and so the methods are inefficient
when there are many alternatives. Procedures in \citeN{kim:2011},
\citeN{dieker:2012} do not use Bonferroni's inequality 
when there are only three alternatives, but again use Bonferroni's inequality when 
comparing more than three alternatives.

@@

To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.  Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \cite{Frazier:BIZ}.
We conjecture that a proof technique similar to the one presented here can be used to show asymptotic validity of the BIZ procedure when
the variances are unknown, and we present numerical experiments that support this belief.

@@

Ranking and Selection is a problem where we have to select the best system
among a finite set of alternatives, i.e. the system with the largest
mean. The method selects a system as the best based on the samples
that are observed sequentially over time. We suppose that samples
are identically distributed and independent, over time and across alternatives, and
each alternative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.

@@

The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given below.  It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$.
$B_{x}$ controls the number of samples taken from system $x$ in
each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$. Numerical experiments on 
common cases show little difference in the PCS between the version of BIZ
we analyze and the version in \cite{Frazier:BIZ}.

@@

This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).

@@

@@

\begin{lemma}
Let $x\in\left\{ 1\ldots,k\right\} $, then
\[
\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
\]
as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
is a standard Brownian motion.
\end{lemma}

@@

To accomplish the first part, for each $F\in D\left[0,\infty\right)^{k}$, 
we define $q_{tx}^{F,\delta}\left(A\right)$ as
\[
q_{tx}^{F,\delta}\left(A\right)=q'\left(\left(F_{x}\left(t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Note that if we replace $F$ by $\mathcal{C}\left(\delta,t\right)$,
we get $q_{tx}\left(A\right)$ in \eqref{eq:q}.

To accomplish the second and third parts, we define
$f\left(F,\delta\right)$ to be obtained by applying the BIZ selection map $h$ to the process
$\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$, and then reporting whether the selection was correct.
More precisely, $f(F,\delta)$ is defined to be
\begin{eqnarray*}
f\left(F,\delta\right) & = & \begin{cases}
    1 & \text{if $h\left(\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
0 & \text{otherwise.}
\end{cases}
\end{eqnarray*}

We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ} 
to a transformed problem that does not depend on $\delta$.

We construct $g$ analogously to $f(\cdot,\delta)$, but we replace the path $q_{tx}^{F,\delta}$ used in the construction of $f(\cdot,\delta)$ by a new path $q_{tx}^{F}$ that doesn't depend on $\delta$, and is obtained by taking the limit as $\delta\to0$.  This path is
\[
q_{tx}^{F}\left(A\right):=\mbox{exp}\left(\frac{F_{x}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x}\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{F_{x'}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x^{'}}\right).
\]
Then, $g$ is defined to be
\begin{eqnarray*}
g\left(F\right) & = & \begin{cases}
    1 & \text{if $h\left(\left(q_{tx}^{F}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
0 & \text{otherwise.}
\end{cases}
\end{eqnarray*}

@@

The following lemma shows that the difference in the correct selection events obtained from applying the BIZ selection map $h$ to the discrete-time and continuous-time versions of $q_{tx}(A)$ vanish as $\delta$ goes to $0$.
A proof of Lemma~\ref{l:interpolation} may be found in a full version of this paper \cite{fullpaper}.

\begin{lemma}
    $\lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
 \mathbb{P}\left(
 f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
 \right)$.

@@

@@

\begin{figure}[h]
  \centering
   \begin{subfigure}[b]{0.3\textwidth}
      \centering
       \includegraphics[width=\textwidth]{plot5.pdf}
    \caption{Known heterogeneous variances, 
        $\lambda^2_k = 0.25$, $\lambda_{1}^2 = 1$, $n_0=0$.
    \label{fig: tahi3}}
   \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{unknown.pdf}
             \caption{
    Unknown highly heterogeneous variances, 
    $\lambda^2_{k} = 100$, $\lambda_{1}^2 = 1$, $n_0=15$.
    \label{fig: tahi2}}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{plot3.pdf}
    \caption{ 
    Known highly heterogeneous variances, 
    $\lambda^2_{k} = 100$, $\lambda_{1}^2 = 1$, $n_0=0$.
        \label{fig: tahi}}
    \end{subfigure}
\caption{
    The PCS of the BIZ procedure versus $\delta$ for three different slippage configurations with 100 alternatives and $P^*=0.9$.
    We observe in all three examples that the PCS converges to $P^*$ as $\delta$ goes to $0$.
    The first example (a) shows typical behavior, where the PCS is above $P^*$ for all values of $\delta$.
    The second (b) and third (c) examples are atypical, and were chosen specially to illustrate that BIZ can underdeliver on PCS in slippage configurations when $n_0$ is small and the variance of the best alternative is much larger than the variance of the other alternatives.
\label{fig:tahi10}}
\end{figure}

Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration where the variance of the best alternative is 1/4 of the variance of the worst alternative. Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $n_{0}=0$. Figure~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied.  Moreover, the PCS approaches $P^*$ as $\delta$ goes to zero, as predicted by Theorem~\ref{t:main}. When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.

Our third example, illustrated in Figure~\ref{fig: tahi}, uses the same sampling distributions as the second example, but assumes the variances are known, and sets $n_0=0$.
The effect of this change, and especially of setting $n_0$ to $0$, is to cause significant underdelivery on PCS for large values of $\delta$.  
As remarked above, this example was chosen specially to illustrate that BIZ can underdeliver on PCS in slippage configurations when $n_0$ is small, and the variance of the best alternative is much larger than the variance of the worst alternative.  However, as predicted by Theorem~\ref{t:main}, the PCS converges to $P^*$ as $\delta$ grows small, even in this pathological case.

@@

We have proved the asymptotic validity of the Bayes-inspired Zone
procedure \cite{Frazier:BIZ} when the variances are known.
This algorithm takes fewer samples than other IZ procedures, especially for
problems with large numbers of alternatives, and so characterizing when it
satisfies the indifference-zone guarantee is important for understanding when
it should be used in practice.
